Quantum H theorem, variational entropy, and relaxation processes

### 2021-01-25 tex/introduction.tex
cambié las ubicaciones de las citas y agregué unas que faltaban

In contrast, for quantum equilibrium systems, the construction of a framework,
with the same level of
success and universality as the classical version, is still an open problem. For instance,
in order to obtain a complete correspondence principle, between classical mechanics
and quantum mechanics, the quantum analogous of both the Boltzmann $H$-theorem
and the Boltzmann transport equation have not attained a fully accepted form.
In this context, Tolman was one of the earliest physicists to propose a quantum
$H$-theorem \cite{bib:tolman}, using probability transition relations, the random
phases hypothesis, and a spatially homogeneous distribution function.
Also, Tolman proposed a potential quantum analogous of the transport equation,
in terms of the occupation number,
by applying time perturbation theory. Further attempts, under the quantum operator
formalism, have addressed the description of quantum transport phenomena by means of the Hamiltonian
of the system and the master equation (which here is the analogous
of the Boltzmann transport equation)
\cite{bib:gorban2014,bib:bennaim2017,bib:tolman,bib:li2019}. However, these approaches 
are not consistent with the classical-quantum correspondence principle.
In the same line of thought, some authors have proposed $H$-functionals
and attempted to proof a
quantum $H$-theorem \cite{bib:silva2010,bib:deroeck2006,bib:grabert1974}.
However, whether or not the homogeneous distribution function hypothesis is assumed, or
if their framework obeys the correspondence principle is unclear or not discussed whatsoever.
Furthermore, the general validity
of the quantum $H$-theorem, the second law of thermodynamics, and the
interpretation of the quantum entropy is still in discussion %[19-26].
\cite{bib:silva2010,bib:deroeck2006,bib:grabert1974,bib:acharya2019,%
bib:kastner2017,bib:gring2012,bib:han2015,bib:das2018}.

@@

In addition, some aspects regarding the classical $H$-theorem and the
Boltzmann $H$-functional require to be revised, for the purpose of improving their mutual consistency.
For example, the modification of the $H$-theorem to include phenomena stemming from stochastic
trajectories, violations of the second law of thermodynamics, and the relation
between Shannon's measure of information and the Boltzmann's entropy
\cite{bib:nemilov2018,bib:keizer1987,bib:onsager1931,bib:brown2008,bib:dragoljub2009}.

>>>>

In contrast, for quantum equilibrium systems, the construction of a framework,
with the same level of
success and universality as the classical version, is still an open problem. For instance,
in order to obtain a complete correspondence principle, between classical mechanics
and quantum mechanics, the quantum analogous of both the Boltzmann $H$-theorem
and the Boltzmann transport equation have not attained a fully accepted form.
In this context, Tolman was one of the earliest physicists to propose a quantum
$H$-theorem \cite{bib:tolman}, using probability transition relations, the random
phases hypothesis, and a spatially homogeneous distribution function.
Also, Tolman proposed a potential quantum analogous of the transport equation,
in terms of the occupation number,
by applying time perturbation theory. Further attempts, under the quantum operator
formalism, have addressed the description of quantum transport phenomena by means of the Hamiltonian
of the system and the master equation (which here is the analogous
of the Boltzmann transport equation)
\cite{bib:grabert1974,bib:wang2014,%
bib:angel2017,
bib:amato2020,bib:nicacio2015,bib:hussein2014}. However, these approaches 
are not consistent with the classical-quantum correspondence principle.
In the same line of thought, some authors have proposed $H$-functionals
and attempted to proof a
quantum $H$-theorem \cite{bib:gorban2014,bib:bennaim2017,bib:silva2010,%
bib:deroeck2006,bib:acharya2019,bib:kastner2017,bib:han2015,bib:das2018,bib:vonneumann2010}.
However, whether or not the homogeneous distribution function hypothesis is assumed, or
if their framework obeys the correspondence principle is unclear or not discussed whatsoever.
Furthermore, the general validity
of the quantum $H$-theorem, the second law of thermodynamics, and the
interpretation of the quantum entropy is still in discussion %[19-26].
\cite{bib:silva2010,bib:acharya2019,bib:kastner2017,bib:han2015,bib:brown2008,%
bib:dragoljub2009,bib:vonneumann2010,%
bib:syros1999,bib:lesovik2016,
bib:lesovik2019}.

@@

In addition, some aspects regarding the classical $H$-theorem and the
Boltzmann $H$-functional require to be revised, for the purpose of improving their mutual consistency.
For example, the modification of the $H$-theorem to include phenomena stemming from stochastic
trajectories, violations of the second law of thermodynamics, the relation
between Shannon's measure of information and the Boltzmann's entropy, 
and calculation of thermodynamical quantities and thermalization for some systems
\cite{bib:gorban2014,bib:li2019,bib:gring2012,bib:nemilov2018,bib:wang2014}.
